% ---
% Title: Resume
% Author: Weston Odend'hal
% Date: 2020-08-06
% ---

\documentclass{article}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage[T1]{fontenc}

% Package settings
\pagenumbering{gobble}
\titleformat{\section}{\raggedright\bf}{}{0em}{}[\titlerule]
\geometry{
  letterpaper,
  left=0.5in,
  right=0.5in,
  top=0.5in,
  bottom=0.5in
}

% Custom commands
\renewcommand{\familydefault}{phv}
\newcommand{\beginResumeList}{\begin{itemize}\setlength\itemsep{0em}\begin{minipage}{0.9\textwidth}}
\newcommand{\resumeListEnd}{\end{minipage}\end{itemize}}
\newcommand{\boldItem}[2]{\normalsize\item{\textbf{#1}{: #2}}}
\newcommand{\normalItem}[1]{\normalsize\item{#1}}
\newcommand{\experience}[2]{
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \normalsize\textbf{#1} & \normalsize #2 \\
  \end{tabular*}
}
\newcommand{\education}[3]{
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \normalsize\textbf{#1, }\textit{#2} & \normalsize #3 \\
  \end{tabular*}\vspace{-10pt}
}
\newcommand{\social}[3]{
  \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}} c@{\extracolsep{\fill}} r}
    \normalsize{#1} & \normalsize{#2} & \normalsize{#3}
  \end{tabular*}
}
\newcommand{\project}[3]{
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \normalsize\textbf{#1} & \normalsize{#2} \\
    \normalsize\textit{#3}
  \end{tabular*}
}

\begin{document}
  \centering\huge\textbf{Weston Odend'hal}
  \vspace*{0.1in}

  \normalsize \textbf{+1-415-539-6833 | \href{mailto:wodend@tuta.io}{wodend@tuta.io} | San Francisco}
  \vspace*{0.1in}

  \social
    {\textbf{GitHub:} \href{https://github.com/wodend/}{github.com/wodend}}
    {\textbf{LinkedIn:} \href{https://www.linkedin.com/in/wodend/}{linkedin.com/in/wodend}}
    {\textbf{AngelList:} \href{https://angel.co/u/wodend}{angel.co/u/wodend}}

  \section{TECHNICAL SKILLS}
  \beginResumeList
  %\boldItem{Proficient}{Python, NumPy, SciPy, Pandas, multiprocessing, Matplotlib, OpenCV, requests, statsmodels, BeautifulSoup, Jupyter Notebook/Lab, R, Plotly, C/C++, Bash, Linux, Git, GitLab CI/CD, Docker, DigitalOcean, Java, Maven, Tablesaw, Jakarta EE, Selenium, Pandoc, \LaTeX, HTML, SQL, LDAP, PowerShell}
  \boldItem{Proficient}{Python, NumPy, SciPy, Pandas, multiprocessing, Matplotlib, BeautifulSoup, R, C/C++, Bash, Linux, Git, CI/CD, Docker, DigitalOcean, Java, Maven, Jakarta EE, Selenium, Pandoc, \LaTeX, HTML, SQL, LDAP, Spark, PHP/Hack, Presto, React}
  \boldItem{Exposure}{Django, bqplot, C\#, .NET, CSS, Gradle, LXD, Scala, Lua, Javascript/Typescript, SAS, Airflow}
  \resumeListEnd

  \section{WORK EXPERIENCE}
  \experience
    {Facebook | Data Engineer | San Francisco, CA}
    {Oct. 2020 - Present}
    \beginResumeList
      \normalItem{Helped design and implement data pipelines to produce billion-scale training data pool tables to sample from for annotation projects.}
      \normalItem{Wrote pipelines for taking sophisticated stratified responsible AI samples for annotation at the hundreds-of-millions scale.}
      \normalItem{Designed React GUIs for facilitating the annotation of computer vision datasets for supervised learning.}
      \normalItem{Implemented libraries for calculating common computer vision metrics such as AUC and MAP on large-scale datasets.}
    \resumeListEnd

  \experience
    {Deloitte | Data Engineer | San Francisco, CA}
    {Jul. 2019 - Jul. 2020}
    \beginResumeList
      \normalItem{Created data pipeline to aggregate and clean user login data across a distributed environment with PowerShell scripts and LDAP database queries, reducing time spent 50\% and including previously unavailable data.}
      \normalItem{Automated analysis of user login data with a Java program using the Tablesaw library to generate daily and weekly login statistics, reducing time spent by 90\%.}
      \normalItem{Introduced a new process to generate security scan crawls using Selenium, saving the client \$12,000 per month.}
      \normalItem{Generated sanitized test data using IBM Optim to obfuscate Personally Identifying and Protected Health information from the production SQL Server database with over 100,000,000 records for 450,000+ users.}
    \resumeListEnd

  \experience
    {Cal Poly | Teaching Assistant (Computer Science) | San Luis Obispo, CA}
    {Sep. 2018 - Jun. 2019}
    \beginResumeList
      \normalItem{Led office hours for a new class, helping students work through statistics and machine learning assignments using Pandas, NumPy, statsmodels, and SciKit-Learn for over 60 students.}
      %\normalItem{Took questions in class on general programming concepts such as data structures, web scraping, computational complexity, and regular expressions.}
      \normalItem{Troubleshoot issues including Python dependency problems, and explain solutions to students.}
    \resumeListEnd

  \experience
    {Cal Poly | Data Engineer (Research) | San Luis Obispo, CA}
    {Jun. 2017 - Jun. 2018}
    \beginResumeList
      \normalItem{Cleaned and curated SAS datasets downloaded from the Panel Study of Income Dynamics, allowing researchers to access 100+ of GB's of previously unavailable data.}
      \normalItem{Automated determination of optimal office hours for professors with a tool written in R using matrix algebra, saving 90\% of time spent scheduling each quarter.}
      \normalItem{Created a custom PDF scraping tool in C using the Poppler library to facilitate research, allowing us to include critical factors that were necessary for our linear regression.}
    \resumeListEnd

\section{EDUCATION}
  \education
    {B.S. Economics; Minor Computer Science}
    {California Polytechnic State University}
    {Jun. 2019}

\section{PROJECT WORK}

  %\project
  %  {Home Lab | DevOps Engineer | \href{https://github.com/wodend/cloudflare-ddns}{github.com/wodend/cloudflare-ddns}}
  %  {Jun. 2019 - Present}
  %  {Host infrastructure for personal projects, and learning new technologies.}
  %  \beginResumeList
  %    \normalItem{Hosted dockerized personal GitLab source control and GitLab pages behind HAProxy load balancer.}
  %    \normalItem{Automated LetsEncrypt certificate renewal with DNS verification challenge using Cloudflare's API.}
  %    \normalItem{Generated static HTML pages with MathJax for LaTeX using Pandoc Markdown.}
  %    \normalItem{Managed subnet with DDWRT router using dnsmasq for local DNS, and DNS filtering.}
  %    \normalItem{Operated physical Debian and Gentoo Linux infrastructure for hosting dockerized applications.}
  %  \resumeListEnd

  \project
    {PySimplePlotter | Software Engineer | \href{https://github.com/wodend/pysimpleplotter}{github.com/wodend/pysimpleplotter}}
    {Apr. 2021 - Present}
    {Plot output from scientific instruments quickly and easily with a simple GUI.}
    \beginResumeList
      \normalItem{Implemented file reader to automatically detect, clean, and read various delimited file formats.}
      \normalItem{Wrote a tool using pandas and matplotlib which allows the user to visualize plots of multiple relationships and export the output.}
      \normalItem{Designed a GUI interface to matplotlib's API to allow the user to customize the plot.}
    \resumeListEnd

  %\project
  %  {Differentials by Location | Data Engineer | \href{https://github.com/wodend/hotel-scraper}{github.com/wodend/hotel-scraper}}
  %  {Feb. 2019 - Jun. 2019}
  %  {Model price differences by region with data scraped from hotel websites.}
  %  \beginResumeList
  %    \normalItem{Created scraping tools for travel websites using Beautiful Soup in Python to get price data on over 300 hotels at once from 3 different travel websites and 8 different regions.}
  %    \normalItem{Scheduled multi-threaded execution of scraping at specified intervals with shell scripts deployed on DigitalOcean droplets to comply with rate limits and gather data across time.}
  %    \normalItem{Created linear models based on pricing for each region, and used ANOVA analysis to determine statistical significance of differences in pricing based on region.}
  %  \resumeListEnd
  %\project
  %  {CPF2CSV | Research Assistant | \href{https://github.com/wodend/cpf2csv}{github.com/wodend/cpf2csv}}
  %  {2018}
  %  {Converts unstructured PDF degree flowchart data from Cal Poly to machine-readable CSV.}
  %  \beginResumeList
  %    \normalItem{Cropped degree flowcharts into regions for each of the quarters listed with the Poppler PDF library.}
  %    \normalItem{Generated .csv output containing the list of requirements for each quarter listed on the degree flowchart.}
  %    \normalItem{Output from the program used in research on the efficiency of class scheduling and assignment at a public university.}
  %  \resumeListEnd

%\section{LEADERSHIP + AWARDS}
%  \education
%    {Treasurer}
%    {Cal Poly Economics Society}
%    {Jun. 2019}
%  \education
%    {Eagle Scout}
%    {Boy Scouts of America}
%    {Jun. 2015}

\end{document}
